Reproducible Research Practices and Barriers to Reproducible Research in Geography: Insights from a Survey

### 2022-12-14 docs/manuscript/manuscript.tex
Adjusted Results Plan

\begin{itemize}
    \item Include a comparison of sample to the sample frame along the dimensions available from the frame. (Table 0)
    \item Include a summary of the key in sample characteristics (Table 1?). Rows - Title, Citations (pulled from frame), Gender; cols - methods and subfields. \textcolor{red}{Does this need to be a table? I am not sure any of these demographics really matter to our analysis. That is unless we plan to look at some measure across seniority or 'impact', which we could do.}
\end{itemize}

@@

\subsubsection*{Definition of Reproducibility}
\begin{itemize}
    \item Self-reported definition (Q6) analysis.
    \item Interpretations of reproductions (Q8) - focus on Q8a, Q8b, Q8e as these provide the most direct information about how a respondent processes the evidence provided by a reproduction. Match Q8e with 17c, 17e, 17f which are importance questions about credibility. Match Q8b with 17a which are both about validity. 
    \item Importance of reproducibility (Q17) - Reproducibility was/wasn't seen as important for other goals - error reduction (17b), effort duplication (17d), scientific communication (17g, 17h), training (17i, 8d).
    \item Reproducibility Estimate (Q13) - \textcolor{red}{What is the state of the summaries on this dimension?}
\end{itemize}

@@

>>>>

\begin{itemize}
    \item Include a text summary of the key in sample characteristics summarized in Table 1a and 1b.
\end{itemize}

@@

@@

\subsection*{Definition of Reproducibility}
\begin{itemize}
    \item Self-reported definition (Q6) analysis: Qualitative analysis that will present a typology of definitions by combination of the Q,Q,M and M,P,NS,H splits that match on the 8 category coding of the provided definitions. 
    \item Interpretations (Q8) and Importance (Q17) of reproductions: Develop a split that distinguishes between Qs that focus on epistemology Q8a+Q8b+Q8f+17a, as these provide the most direct information about how a respondent processes the evidence provided by a reproduction; and Qs that focus on reproducibility as a quality of a study Q8e+Q8c+17c+17e+17f. We will explore how these question groups crosstab with the typologies we draw from Q6. Initial assumption is that many will support reproduction as a study characteristic or label, and less will link it with epistomological function. Examine by subfields and methods, which we expect to align with typologies from Q6. 
    \item Importance of reproducibility (Q17) - Reproducibility was/wasn't seen as important for other open science goals - error reduction (17b), effort duplication (17d), scientific communication (17g, 17h), training (17i, 8d).
    \item Reproducibility Estimate (Q13) - \textcolor{red}{What is the state of the summaries on this dimension?}
\end{itemize}
